\chapter{Conclusion} \label{chap:conclusion}
  The~goal of this thesis to develop a library for a remote control of e-Puck 
  over Bluetooth was successfully accomplished.
  The implemented {\it Elib} library offers a~comfortable interface for asynchronous programming,
  which allows programmers to create a~more sophisticated application like {\it Epuck Joystick}.
  
  The library is well documented and several model examples introduce in detail
  a usage of {\it Elib library}.
  Graphical application {\it Epuck Joystick} clearly introduces all sensors and actuators of e-Puck. 
  It gives a user possibility to explore e-Puck's capabilities without programming.
  In addition, source code of {\it Epuck Joystick} gives programmers a guide 
  how to implement a graphical application for a program 
  that uses asynchronous programming in {\it Elib}. 

  Enclosed {\it Elib Tools} application enables to analyze
  programs that use {\it Elib}.
  It is a command line application, which can parse a~log from commands sent 
  to~e-Puck and collect information from the~log.
  The source code of the application is also commented and 
  the~{\it Elib Tools} program is ready to be extended 
  or modified according to the~needs of programmers that use {\it Elib}.
  
  All programs are written in $C\#$.  $C\#$ programming language
  allows {\it Elib} to implement help for intellisense,
  which is very popular among programmers using Microsoft Visual Studio IDE,
  as well as Monodevelop IDE. {\it Elib} library can run on Linux due to
  Mono runtime, as well on Windows due to .Net runtime.
  Last but not least, $C\#$ language is easy to learn 
  and many of students already program in $C\#$.

  A remote control of e-Puck over Bluetooth, implemented in {\it Elib} library, 
  has been tested on the~enclosed model program {\it TestElib}. 
  Tests have shown, that the~communication used by {\it Elib} is fast enough
  to control an e-Puck robot.

  As a whole, the {\it Elib library} tries to offer a programmer
  of e-Puck as much comfort as possible.

